\pkg{casebase}: An Alternative Framework For Survival Analysis

### 2020-07-19 analysis/paper/paper.Rmd
trying to get scales to work

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  cache = TRUE, 
  comment = "#>",
  fig.path = "../figures/"
)
options(kableExtra.latex.load_packages = FALSE)
library(casebase)
library(colorspace)
library(cowplot)
library(scales)
library(data.table)
library(glmnet)
library(kableExtra)
library(magrittr)
library(pracma)
library(flexsurv) # for fitting gompertz AFT
library(prodlim)
library(riskRegression)
library(splines)
library(survival)
library(tibble)
library(visreg)
library(lubridate)
library(tidyverse)
options(digits = 2, scipen = 999)
# set the seed for reproducible output
set.seed(1234)

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  cache = TRUE, 
  comment = "#>",
  fig.path = "../figures/"
)
options(kableExtra.latex.load_packages = FALSE)
library(casebase)
library(colorspace)
library(cowplot)
library(data.table)
library(glmnet)
library(kableExtra)
library(magrittr)
library(pracma)
library(flexsurv) # for fitting gompertz AFT
library(prodlim)
library(riskRegression)
library(splines)
library(survival)
library(tibble)
library(visreg)
library(lubridate)
library(tidyverse)
library(scales)
options(digits = 2, scipen = 999)
# set the seed for reproducible output
set.seed(1234)
